SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v19]

### 2015-09-07 paper.tex
updated figures, added limitations

\newboolean{include-notes}
\setboolean{include-notes}{true}
\newcommand{\adnote}[1]{\ifthenelse{\boolean{include-notes}}%
 {\textcolor{blue}{\textbf{AD: #1}}}{}}

 \newcommand{\fpnote}[1]{\ifthenelse{\boolean{include-notes}}%
 {\textcolor{blue}{\textbf{FP: #1}}}{}}

  \newcommand{\mlnote}[1]{\ifthenelse{\boolean{include-notes}}%
 {\textcolor{purple}{\textbf{ML: #1}}}{}}

@@

\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v17]}

@@

\begin{abstract}
Online algorithms for robot model-free robot learning from demonstration (such as DAgger) can learn policies for problems where the system
dynamics and the cost function are unknown. However, during learning they impose a burden on supervisors to provide labels (control
signals) as the robot encounters new states when iteratively executing its current best policy. We introduce the SHIV
algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to \emph{only request supervision for risky states}. SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary high dimensional state distributions.  To facilitate scaling and outlier rejection, risk is based on distance to an approximate level set boundary defined by a One Class support vector machine.  We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator with a 27936D visual HOG feature state representation, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D) with a 22D state representation  of joint angles and the pose of each object, and 3) surgical needle insertion with a 16D state represented spatial transform.  Results suggest that SHIV can reduce the number of queries up to 70$\%$\adnote{double check this}.

@@

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/teaser.pdf}
\caption{ 
SHIV  reduces the number of queries to the supervisor in our three test domains: a) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; b) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; c) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery; d) cost of SHIV and DAgger's policy on the grasping in clutter example versus states labeled.
}
\vspace*{-10pt}
\label{fig:teaser}
\end{figure}

@@

We assume a known state space and set of controls. We assume access to a robot or simulator, such that we  can sample from the state sequences induced by a sequence of controls.   Lastly, we assume access to a supervisor who can, given a state, provide the desired control signal label.

@@

The decision function parametrization consists of the kernel bandwidth $\sigma$ in $g_s$. Changing sigma corresponds to how much influence each point in the training set has on the measure of risk. Large $\sigma$ corresponds to points nearby being safe.

@@

We then compare SHIV and DAgger on three domains: a driving simulator, push-grasping in clutter with a 4DOF arm, and surgery needle insertion using demonstrations from Dr. Douglas Boyd, a master surgeon at UC Davis.

@@

\noindent\textbf{Driving Simulator Domain.}
Our first domain is a common benchmark in Reinforcement Learning: learning a policy for a car to drive around a track~\cite{argall2009survey,ross2010efficient,ross2011reduction}. We implemented a driving simulator where the car must follow a polygonal track. We generated polygonal tracks by repeatedly sampling from a Gaussian with mean that is the center of the video game workspace centered in the middle of the workspace, and computing the convex hull of the sampled points.Then a convex hull is computed on the sampled points. In general this produces tracks composed of five to seven edges, an example is shown in Fig. \ref{fig:teaser}(a). If the car accidentally leaves the track, it is placed
back on the center of the track at a nearby position. The car's control input space is given by  $\mathcal{U} = \lbrace
-15^\circ, 0, 15^\circ \rbrace$. A control input instantly changes the angle of the car which drives at a unit speed. 
The internal state space of the car is given by the
xy-coordinates and the angle it is facing. In our experiments, the supervisor is provided by an algorithm that uses
state space search through the driving simulator to plan the next control.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth, height=6cm]{figures/grasp_clutter.eps}
\caption{We compare performance for Grasping in Clutter in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of objects knocked off the table plus 10 times the binary value indicating if the object is grasped or not. Initial results, which are averaged over 8 different trials suggest a $64\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
\vspace*{-10pt}
\label{fig:grasp_cost}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth, height=6cm]{figures/needle_insertion_results.eps}
\caption{We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is euclidean distance between translation in centimeters. In Fig. \ref{fig:car_cost}, we plot the performance of DAgger and SHIV without the modification.  Initial results, which are run for 20 iterations each and are averaged over 40 different initial starting positions, shown in Fig. \ref{fig:car_cost} suggest an $67\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
\vspace*{-10pt}
\label{fig:needle}
\end{figure}

\section{Discussions and Future Work}
\adnote{as florian says, this needs a lot of work; it needs to start by summarizing the key contribution and results, and it needs to state the limitations clearly -- we've talked a lot about limitations during out in person meetings, hopefully michael took notes; only then you can point to some big areas of future work that actually sounds exciting}
\fpnote{we'll need to work on this}
SHIV currently provides a way to apply active learning to online learning from demonstration, however its use of level set estimation of the underlying distribution introduces several hyper parameters. As Fig. shown these can significantly effect performance if not tuned correctly. Future work will look at using cross validation on a hold out set of data to more effectively tune parameters.

Another potential issue is that each iteration of SHIV requires solving a quadratic program with the Gram matrix. As we scale to harder tasks that require significantly more data, this can become problematic. Future work will look at using techniques like PCA and random feature projections to scale efficiently \todo{cite something}.

Lastly, our approach is promising in simulation. However we need to evaluate how our active learning method will work on a real robot with noisy sensor observations. Future work will be doing the grasping in clutter experiments on an actual robot.

>>>>

\newboolean{include-notes}
\setboolean{include-notes}{true}
\newcommand{\adnote}[1]{\ifthenelse{ \boolean{include-notes}}%
 {\textcolor{blue}{\textbf{AD: #1}}}{}}

 \newcommand{\fpnote}[1]{\ifthenelse{ \boolean{include-notes}}%
 {\textcolor{blue}{\textbf{FP: #1}}}{}}

  \newcommand{\mlnote}[1]{\ifthenelse{ \boolean{include-notes}}%
 {\textcolor{purple}{\textbf{ML: #1}}}{}}

@@

\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v19]}

@@

\begin{abstract}
Online algorithms for robot model-free robot learning from demonstration (such as DAgger) can learn policies for problems where the system
dynamics and the cost function are unknown. However, during learning they impose a burden on supervisors to provide labels (control
signals) as the robot encounters new states when iteratively executing its current best policy. We introduce the SHIV
algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to \emph{only request supervision for risky states}. SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary high dimensional state distributions.  To facilitate scaling and outlier rejection, risk is based on distance to an approximate level set boundary defined by a One Class support vector machine.  We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator with a 27936D visual HOG feature state representation, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D) with a 22D state representation  of joint angles and the pose of each object, and 3) surgical needle insertion with a 16D state represented spatial transform.  Results suggest that SHIV can reduce the number of queries up to 70$\%$.

@@

\begin{figure}[ht]
\centering

\includegraphics[width=0.5\textwidth]{figures/teaser.pdf}
\caption{ 
SHIV  reduces the number of queries to the supervisor in our three test domains: a) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; b) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; c) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery; d) cost of SHIV and DAgger's policy on the grasping in clutter example versus states labeled.
}
\vspace*{-10pt}
\label{fig:teaser}
\end{figure}

@@

@@

We assume a known state space and set of controls. We assume access to a robot or simulator, such that we  can sample from the state sequences induced by a sequence of controls.   Lastly, we assume access to a supervisor who can, given a state, provide a control signal label. We assume the supervisor the supervisor can be noisy and imperfect, but also that the robot can at best reach the same level of performance of the supervisor after learning.

@@

The decision function parametrization consists of the kernel bandwidth $\sigma$ in $g_s$. Changing sigma corresponds to how much influence each point in the training set has on the measure of risk. Large $\sigma$ corresponds to points nearby being safe. For a policy that is a smooth function $\sigma$ should be large.

@@

We then compare SHIV and DAgger on three domains: a driving simulator, push-grasping in clutter with a 4DOF arm, and surgery needle insertion using demonstrations from Dr. Douglas Boyd, a master surgeon at UC Davis. Each domain test different aspects of our algorithm: the driving simulator has a high dimensional visual state space, grasping in clutter has a human demonstrator provide the labels and is a challenging manipulation problem, surgical needle insertion uses data from a real robot and has an expert demonstrator.

@@

\noindent\textbf{Driving Simulator Domain.}
Our first domain is a common benchmark in Reinforcement Learning: learning a policy for a car to drive around a track~\cite{argall2009survey,ross2010efficient,ross2011reduction}. We implemented a driving simulator where the car must follow a polygonal track. We generated polygonal tracks by repeatedly sampling from a Gaussian with mean that is the center of the video game workspace centered in the middle of the workspace, and computing the convex hull of the sampled points.Then a convex hull is computed on the sampled points. In general this produces tracks composed of five to seven edges, an example is shown in Fig. \ref{fig:teaser}(a). If the car accidentally leaves the track, it is placed
back on the center of the track at a nearby position. The car's control input space is given by  $\mathcal{U} = \lbrace
-15^\circ, 0, 15^\circ \rbrace$. A control input instantly changes the angle of the car which drives at a unit speed. 
The internal state space of the car is given by the
xy-coordinates and the angle it is facing. In our experiments, the supervisor is provided by an algorithm that uses
state space search through the driving simulator to plan the next control. The algorithm is only allowed to search a finite amount a time ahead in the game and is prone to error, thus on averages crashes 5 times per lap.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth, height=2in]{figures/grasp_clutter.eps}
\caption{We compare performance for Grasping in Clutter in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of objects knocked off the table plus 10 times the binary value indicating if the object is grasped or not. Initial results, which are averaged over 8 different trials suggest a $64\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
\vspace*{-10pt}
\label{fig:grasp_cost}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth, height=2in]{figures/needle_insertion_results.eps}
\caption{We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is euclidean distance between translation in centimeters. In Fig. \ref{fig:car_cost}, we plot the performance of DAgger and SHIV without the modification.  Initial results, which are run for 20 iterations each and are averaged over 40 different initial starting positions, shown in Fig. \ref{fig:car_cost} suggest an $67\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
\vspace*{-10pt}
\label{fig:needle}
\end{figure}

\section{Discussions and Future Work}
Online imitation learning algorithms have been successful on array of task~\cite{NIPS2014_5421,ross2010reduction}, however can significantly increase the burden on a supervisor. Our algorithm, SHIV, implements stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions. We empirically evaluated our method on three different domains: a driving simulator, grasping in clutter and surgical needle insertion. Results suggest a $70\%$ reduction in the number of queries to the supervisor needed.

While achieving a high level of performance, SHIV has several limitations. For instance, the selection of the value of $\sigma$ can affect performance and a poor choice could result in the algorithm becoming offline imitation learning, as shown in Table \ref{tab:sens}. Future work will look at better understanding the relationship of $\sigma$ to the function $\pi_{\theta}$ and how to automatically select it.

 Furthermore, to update the decision function $g_{\sigma}$ requires solving a quadratic program, which has an upper bound computationally complexity of $O(n^3)$ in the number of data points. This can effect the ability of using our modified One Class SVM for larger problems. Future work will look at using techniques such as random features or PCA on the kernel Gram matrix to allow for better scaling~\cite{scholkopf2002learning}.

 Lastly, online imitation learning only allows a policy to learn to be as good as the supervisor. If the supervisor is imperfect then the robot will be as well. Future work will look at combining techniques from inverse reinforcment learning\cite{argall2009survey} with online imitation learning to allow the robot to improve upon it's policy after supervision is done.
